Comparing Apples and Oranges in Youth Depression Treatments?

### 2024-09-22 multilevel_metaregression/manuscript_with_multilevel_metan.qmd
final analyses before revision submission

    # Calculate variance distribution using the existing function
    i2_results <- dmetar::var.comp(model)

@@

 png("plot_means_multi_all.png")
 plot_means_multi_all
 dev.off()
```

@@

# Assign new column names to the data frame
colnames(aggregate_results_overall) <- new_column_names

table_aggregate_results_overall <- aggregate_results_overall[, 1:6]
table_aggregate_results_overall[1, 4] <- NA

flextable(table_aggregate_results_overall) %>%
  set_table_properties(width = 1) %>%
  autofit() %>%
  add_footer_row(values = as_paragraph("T", as_sup("2"), as_sub("L3"), " = ", aggregate_results_overall[1, "T2_1"], ";", as_i("T"), as_sup("2"), as_sub("L2"), " = ", aggregate_results_overall[1, "T2_2"],
                      "; ", as_i("I"), as_sup("2"), as_sub("L3"), " = ", aggregate_results_overall[1, "I2_3"], 
                      "; ", as_i("I"), as_sup("2"), as_sub("L2"), " = ", aggregate_results_overall[1, "I2_2"], 
                      "; ", as_i("K"), " = ", aggregate_results_overall[1, "k"], "."), colwidths = 6) %>%
  # add_header_row(values = "Results from metaregression with overall sample", colwidths = 6) %>%
  # add_header_row(values = "Table 4", colwidths = 6) %>% 
  bold(part = "header") %>%   # Bold the relevant header rows
  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
  # italic(i = 2, italic = TRUE, part = "header") %>% 
  border_remove() %>% # this is to remove borders around the caption that look strange
  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
  vline(j = 1, part = "body", border = small_border) %>% 
  border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
  hline(part = "header", border = big_border) %>% 
  # padding(i = 2, padding.bottom = 15, part = "header") %>% 
  align(j = 2:ncol(table_aggregate_results_overall), align = "center", part = "all") %>% 
  align(j = 1, align = "left", part = "all") %>% 
  font(fontname = "Calibri", part = "all") %>% 
  paginate(init = TRUE, hdr_ftr = TRUE) %>% 
  line_spacing(space = .7, part = "all")
```

>>>>

    # Calculate variance distribution using the existing function
    i2_results <- var.comp(model)

@@

@@

# Assign new column names to the data frame
colnames(aggregate_results_overall_i2) <- new_column_names

table_aggregate_results_overall_i2 <- aggregate_results_overall_i2[, 1:6]
table_aggregate_results_overall_i2[1, 4] <- NA

flextable(table_aggregate_results_overall_i2) %>%
  set_table_properties(width = 1) %>%
  autofit() %>%
  add_footer_row(values = as_paragraph("T", as_sup("2"), as_sub("L3"), " = ", aggregate_results_overall_i2[1, "T2_1"], ";", as_i("T"), as_sup("2"), as_sub("L2"), " = ", aggregate_results_overall_i2[1, "T2_2"],
                      "; ", as_i("I"), as_sup("2"), as_sub("L3"), " = ", aggregate_results_overall_i2[1, "I2_3"], 
                      "; ", as_i("I"), as_sup("2"), as_sub("L2"), " = ", aggregate_results_overall_i2[1, "I2_2"], 
                      "; ", as_i("K"), " = ", aggregate_results_overall_i2[1, "k"], "."), colwidths = 6) %>%
  # add_header_row(values = "Results from metaregression with overall sample", colwidths = 6) %>%
  # add_header_row(values = "Table 4", colwidths = 6) %>% 
  bold(part = "header") %>%   # Bold the relevant header rows
  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
  # italic(i = 2, italic = TRUE, part = "header") %>% 
  border_remove() %>% # this is to remove borders around the caption that look strange
  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
  vline(j = 1, part = "body", border = small_border) %>% 
  border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
  hline(part = "header", border = big_border) %>% 
  # padding(i = 2, padding.bottom = 15, part = "header") %>% 
  align(j = 2:ncol(table_aggregate_results_overall_i2), align = "center", part = "all") %>% 
  align(j = 1, align = "left", part = "all") %>% 
  font(fontname = "Calibri", part = "all") %>% 
  paginate(init = TRUE, hdr_ftr = TRUE) %>% 
  line_spacing(space = .7, part = "all")
```
